Project Report: \\ Detecting Spam on Social Networking Sites

### 2012-05-08 docs/paper/paper.tex
added median

To choose a sample of relevant features, we computed statistics on the extracted features, both on the ham and spam corpora. These statistics were generated using SQL on a table created from the merged and cleaned data generated in the process described above. SQL makes it trivial to calculate means and standard errors, but medians are more resource-intensive, so we omitted them from our

@@

\textbf{Sender IPs:} Spammers in general had a smaller number of unique IP addresses associated with them than ham users, as per figure \ref{fig:uniqip}. The mean for spammers was 11.82 with a standard deviation of 52.52, whereas ham users saw a mean of 175.51 and standard deviation of 322.19. This is likely due to their comparatively low length of time on the site and the fact that many legitimate users are behind NATs that yield a high number of dynamic IP addresses. One possibility for future research is to investigate the ratio of unique IPs for users as a function of the time they have been registered. Likewise, examining unique /16 network blocks instead of unique IP addresses could mitigate the influence of NATs.

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{figures/unique-ips.pdf}
    \caption{Number of unique IP addresses associated with user account. Spam: mean 11.82, std. dev. 52.52. Ham: mean 175.51, std. dev. 322.19}
    \label{fig:uniqip}
\end{figure}

@@

>>>>

To choose a sample of relevant features, we computed statistics on the extracted features, both on the ham and spam corpora. These statistics were generated using SQL on a table created from the merged and cleaned data generated in the process described above.

@@

\textbf{Sender IPs:} Spammers in general had a smaller number of unique IP addresses associated with them than ham users, as per figure \ref{fig:uniqip}. The mean for spammers was 11.82 with a standard deviation of 52.52 and a median of 2, whereas ham users saw a mean of 175.51, a standard deviation of 322.19 and median of 64. This is likely due to their comparatively low length of time on the site and the fact that many legitimate users are behind NATs that yield a high number of dynamic IP addresses. One possibility for future research is to investigate the ratio of unique IPs for users as a function of the time they have been registered. Likewise, examining unique /16 network blocks instead of unique IP addresses could mitigate the influence of NATs.

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{figures/unique-ips.pdf}
    \caption{Number of unique IP addresses associated with user account. Spam: mean 11.82, std. dev. 52.52, median 2. Ham: mean 175.51, std. dev. 322.19, median 64}
    \label{fig:uniqip}
\end{figure}

@@

- plan to implement SVM, despite speed tradeoff
